Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-28 research_proposal/research_proposal.qmd
fix YAML header

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    include-in-header: 
      text: |
        \usepackage{bm}
---

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    # include-in-header: 
    #   text: |
    #     \usepackage{bm}
    #     \usepackage{amsmath}
    mathspec: true
    number-sections: true
---
